%-------------------------
% Resume
% Author : Drew Johnson
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% List indent 
\setlist{leftmargin=*}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------

% Custom commands
\newcommand{\overviewSection}[1]{%
  \begin{center}
    \small #1 \par
  \end{center}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemTitle}[1]{\textbf{#1}:}


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://drewj.dev/}{\Large Drew Johnson}} & Email : \href{mailto:DrewJohnsonGT@gmail.com}{DrewJohnsonGT@gmail.com}\\
%   \href{http://drewj.dev/}{drewj.dev} & Mobile : +1-404-825-2866 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Drew Johnson} \\ \vspace{1pt}
	\small 404-825-2866 $|$ \href{mailto:x@x.com}{\underline{DrewJohnsonGT@gmail.com}} $|$ 
	\href{https://linkedin.com/in/drewjohnsongt}{\underline{linkedin.com/in/drewjohnsongt}} $|$
	\href{https://github.com/drewjohnsongt}{\underline{github.com/drewjohnsongt}} $|$
	\href{https://drewj.dev/}{\underline{drewj.dev}}
\end{center}

%-----------OVERVIEW-------------

\overviewSection {Accomplished Senior Software Engineer and Team Lead with over 8 years of experience specializing in full-stack development, cloud architecture, and big data solutions. Proven leadership in guiding teams of 5-8 engineers through the full product lifecycle at a high-growth unicorn cybersecurity startup. Experience in building, upgrading, and maintaining systems at the scale of Fortune 100/500 companies. Lifelong learner, always building something.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages:}{ TypeScript/JavaScript, Python, Scala, Java, GraphQL, SQL, Terraform, HTML/CSS} \\
		\textbf{Frameworks/Tools:}{ React, Node.js, AWS, GCP, Azure, Docker, Spark, Databricks, Tailwind CSS, Shadcn/UI} \\
		\textbf{Skills:}{ Cloud Native Development, Full Stack Development, IaC, CI/CD and DevOps, data engineering}
        }}
\end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Staff Software Engineer}{Jul 2024 -- Present}
{Log10}{San Francisco, CA (Remote)}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Technical Leadership} Led application development at seed-stage AI startup, as the primary engineer responsible for frontend architecture, API design, and deployment strategies, supporting rapid product iterations and pivots.}
\resumeItem{\resumeItemTitle{Full Stack Development} Migrated Next.js-based REST API to robust, end-to-end typesafe GraphQL architecture, improving developer productivity and cutting feature implementation time by 50\%.}
\resumeItem{\resumeItemTitle{Greenfield Product Development} Spearheaded development of a new HIPAA and SOC II compliant AI-driven document builder, including Terraform-based AWS deployment, GraphQL APIs, and gRPC integration.}
\resumeItemListEnd

\resumeSubheading
{Team Lead and Senior Software Engineer}{Feb 2021 -- Jul 2024}
{JupiterOne}{Raleigh, NC (Remote)}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Project Leadership} Led both technical and non-technical aspects of a teams of up to 8 engineers, translating ambiguous requirements into technical system designs and actionable implementation plans.}
\resumeItem{\resumeItemTitle{Full Stack System Design} Drove SaaS architecture and development to support 1000\%+ company growth, using React single-SPA microfrontends and serverless, multi-tenant, and asynchronous/event-driven AWS patterns.}
\resumeItem{\resumeItemTitle{Big Data Engineering} Designed and implemented a high-throughput (25B records/hour) deduplication ETL system using Spark/Scala/Databricks, which consolidates CDC Delta Lake data, securing 1m+ ARR deal.}
\resumeItem{\resumeItemTitle{AI/LLM} Championed the integration of AI and LLMs into the JupiterOne platform, leading the development of a feature that transforms natural language queries into a cipher-based DSL, increasing user engagement by over 400\%.}
\resumeItemListEnd

\resumeSubheading
{Senior Software Engineer}{May 2020 -- Feb 2021}
{The Home Depot}{Atlanta, GA (Remote)}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Full Stack Typescript} Authored suite of new React frontends and Node/Express/TypeORM layered multi-tenant microservice APIs for B2B/B2C tax exemption software, decreasing monthly legacy system requests by 2 million.}
\resumeItem{\resumeItemTitle{Cloud Architecture and SRE} Directed GCP cloud architecture, CI/CD, and database migrations from legacy on-premise systems to new microservice architecture maintaining 99.99\% uptime for 250k+ requests a day. } 
\resumeItemListEnd

\resumeSubheading
{Senior Software Engineer}{Sep 2019 -- May 2020}
{Delta Air Lines}{Atlanta, GA}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Cloud Architecture} Guided development architecture of Delta’s first AWS cloud project, implementing real-time, high throughput data streaming from on-premise sources for the daily distributed processing of millions of records.}
\resumeItem{\resumeItemTitle{Data Ingestion and Streaming} Integrated with hundreds of disparate legacy on-premise and cloud applications for real-time customer data ingestion, standardization, and consolidation around centralized IDs (SVOC).}
\resumeItemListEnd

\resumeSubheading
{Full Stack Software Engineer (Side contract)}{Oct 2018 -- Sep 2019}
{Schenck Process}{Kansas City, MO}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Full Stack App Design/Development} Architected, developed, and implemented engineering product specification/sizing tool, saving hundreds of monthly engineer hours and preventing company liability issues.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Oct 2017 -- Sep 2019}
{Meridian Business Services}{Overland Park, KS}
\resumeItemListStart
\resumeItem{\resumeItemTitle{Development Lead} Led development efforts supporting company’s 2-year 500\% growth, establishing and maintaining core engineering best practices while delivering effective and efficient code.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Georgia Institute of Technology}{Atlanta, GA}
{Bachelor of Science in Computer Science}{Aug. 2013 -- May 2017}
\resumeSubHeadingListEnd
%


%-------------------------------------------
\end{document}